A radiocarbon data based evaluation of Cultural Transmission in Bronze Age burial rites of Central, Northern and North-western Europe

### 2018-12-09 article/02_Materials_and_Methods.Rmd
added map figure to document

7. Manually defining a rectangular (EPSG:102013) research area with sufficient information in Central-, Northern and Northwestern Europe based on perceived spatial date distribution (Figure **TODO**).

>>>>

7. Manually defining a rectangular (EPSG:102013) research area with sufficient information in Central-, Northern and Northwestern Europe based on perceived spatial date distribution (Figure \ref{map}).

\begin{figure}
\centering
\includegraphics[width=\columnwidth]{../analysis/figures/map.jpeg}
\caption{\label{map}This is a figure.}
\end{figure}
